---
output: 
  html_document:
    fig_caption: yes
  pandoc_args: [
      "--number-sections",
      "--number-offset=1"
    ]

header-includes:
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \usepackage{longtable}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[printwatermark]{xwatermark}

params:
  dat_data: NA
  dat_file: NA

---
<style type="text/css">

h1.title {
  font-size: 24px;
  font-weight: normal;
}
h3 {
  font-weight:normal;
}
.reveal section img { 
  background:none; 
  border:none; 
  box-shadow:none; 
  }
  
  
.watermark {
  opacity: 0.2;
  position: fixed;
  top: 20%;
  left: 50%;
  font-size: 500%;
  -webkit-transform: rotate(-45deg);
  -moz-transform: rotate(-45deg);
  align: center
  color: #00407d;
}  
  
</style>

<div class="watermark">
BEDROCK STAT ANALYTICS
(PAY TO REMOVE)
</div>

```{r include=F}
knitr::opts_chunk$set(comment = NA)
```

```{r,echo=F,warning=F,message=F, error=F}
library(caret)
library(knitr)
library(elasticnet)
library(DMwR)
library(prettyR)
library(xtable)
library(kableExtra)

```

```{r,echo=F}
dat <- params$dat_data
``` 

```{r cache=F, echo=F}
read_chunk('enet_model.R')
read_chunk('help_functions.R')
```


```{r, results='asis',echo=F}
# Load data file
dat <- params$dat_data
dataIn <- dat
indx <- sapply(dataIn, is.factor)
dataIn[indx] <- lapply(dataIn[indx], function(x) as.numeric(x))
```



# Summary Statistics
```{r  descriptive_stat, results='asis', echo = F, message=F, warning=FALSE}
```

```{r  descriptive_stat_html_table, results='asis', echo = F, message=F}
# Summary of unscaled predictor (x) variables 
```
`r sprintf("Note:\n 
The Mean and Std. Dev. are meaningless for categorical variables.") `

```{r standardize_xy, echo=F}
# standardiize xy variables
```


# Correlations Between Predictors
```{r corr_plot, echo=F, fig.height=12,fig.width=12}
# Plot the correlations between predictors
```


# Tuning Parmenter Selection Using Leave-One-Out Cross Validation
```{r loocv, echo=F, warning = F, fig.width=7,fig.height=6}
# results from Loocv
```
`r sprintf("Note:\n 
From above plot, lambda =%.2f and s =%.2f give the minimum RMSE model."
                        ,best.lambda, best.fraction) `


# Variable Importance
```{r var_importance,results='asis',echo=F,warning=F, fig.width=5,fig.height=5}
```

`r sprintf("Note:\n 
All measures of importance are scaled to have a maximum value of 100.")`


```{r  best_model, echo = F,warning = F}
```

# Model Prediction
```{r predict_price, echo = F, warning = F}
```
```{r predict_price_html, echo = F, warning = F}
```

# Standardized Model Coefficients
```{r  enet_coeff, echo = F, warning = F}
```
```{r  enet_coeff_html_table, echo = F, warning = F}
```
`r sprintf("Notes:\n
1) Errors are not given for the predicted coefficients since it is yet unclear how meaningful the std. errors are in penalized regression.\n   
2) Some predictor varaiables may be set to 0 during and/or maybe entrirely removed from the final model based on the optimum tuning parameter values.\n
3) Please, refer to Zou, H. and Hastie, T. (2005) Regularization and Variable Selection via the Elastic Net. Journal of the Royal Statistical Society, Series B, 67, Part 2, 301-320 for a further explanation.\n")`



